\documentclass[12pt]{report}
\usepackage[a4paper, total={7.3in, 9.7in}]{geometry}
\usepackage{amsmath}
\usepackage{upquote}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{amssymb}

\definecolor{backgroundcolor}{rgb}{1, 1, 1}
\definecolor{commentstyle}{rgb}{0.365, 0.422, 0.475}
\definecolor{keywordstyle}{rgb}{0.6, 0.14, 0.576}
\definecolor{numberstyle}{rgb}{0.5, 0.5, 0.5}
\definecolor{stringstyle}{rgb}{0.77, 0.1, 0.08}

\lstdefinestyle{xcodecolor}{
    backgroundcolor=\color{backgroundcolor},   
    commentstyle=\color{commentstyle},
    keywordstyle=\color{keywordstyle},
    numberstyle=\scriptsize\color{numberstyle},
    stringstyle=\color{stringstyle},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                   
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=xcodecolor}

\usepackage[T1]{fontenc}
\usepackage{cascadia-code}

% Raised Rule Command:
%  Arg 1 (Optional) - How high to raise the rule
%  Arg 2            - Thickness of the rule
\newcommand{\raisedrule}[2][0em]{\leaders\hbox{\rule[#1]{1pt}{#2}}\hfill}

\setlength{\parindent}{0pt}
\titleformat{\section}
{\normalfont\Large\bfseries}{\thesection}{1em}{}[{\titlerule[0.8pt]}]

\begin{document}

	{\Large
	\textbf{It's Not Easy Being Green}}
	
	\vspace{0.4cm}
	DiPS CodeJam 24\raisedrule[0.25em]{1pt}
	\\
	% document

	\section*{Prompt}
	`It's not easy being green,' was the frequent refrain of Kermit the frog. 
	
	`It seems you blend in\\
	With so many other ordinary things,'
	
	he says. Let's find him some friends, shall we? Each input is a string of length $n$ made up of numbers and uppercase letters. Your task is to find the number of 6-character substrings which, when read as a hex colour code, are shades of green. Substrings may overlap with each other.
	
	To determine whether a substring is a shade of green or not, check for the following conditions to be true:
	\begin{itemize}
		\item the amount of blue in the colour is less than 80\% of the amount of green
		\item the amount of red in the colour is less than 64\% of the amount of green
	\end{itemize}
	
	Given a string of length $n$, how many substrings can you find that satisfy the conditions?

	\subsection*{Input Format}
	\begin{itemize}
		\item The first line of the input contains a string of length $n$ containing numbers and uppercase letters.
	\end{itemize}
	\subsection*{Output Format}
	The first and only line of your output must contain a single integer $m$, denoting the the number of substrings that satisfy the conditions.
	\subsection*{Constraints}
	\begin{itemize}
		\item $ 10^4 \le n \le 10^6 $
	\end{itemize}

\section*{Solution}
\begin{itemize}
	\item Start a counter at 0 to count the number of substrings that satisfy the condition
	\item Iterate through every 6-letter substring
	\item Check if the substring is in hexadecimal
	\item If the substring is hexadecimal and satisfies the condition, increment the counter
\end{itemize}


\section*{Sample Program}
\lstinputlisting[language=Python]{sampleSolution.py}
	

\end{document}